---
title: "Exercise 1: R Basics"
output:
  html_document:
    number_sections: yes
    toc: yes
---

# Exercise 1: R Basics 
In this short exercise, you will learn  
(1) How to figure out function parameters from a help doc   
(2) How to create a vector from a function output   
(3) How to extract values in a vector using its index   
(4) How to use simple arithmetic operators in R  

## Find what `sample` function does and what parameters it needs.

```{r}
# Write your answer below
```

## Using the `sample` function, create a vector named `coeffs` containing 3 integers drawn from -10 to 10 inclusively with replacement.

```{r}
# Write your answer below
```

## Determine the class of the vector `coeffs`.

```{r}
# Write your answer here
```

## Create variables, a, b, and c, and assign the 3 values from the vector `coeffs` respectively.

```{r}
# Write your answer below
```

## Evaluate the discriminant of the quadratic equation, which is calculated as (b^2 - 4ac).
```{r}
# Write your answer here
```

